Profile likelihoods for geostatsistical models using GPU's

### 2022-01-09 pkg/oldgpuRandom/inst/doc/L2021_11/paper2.tex
paper2
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@3105 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\caption{\label{tab:swisssummarycompare}Summary comparison}
\centering
\begin{tabular}[t]{rcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{geostatsp} & \multicolumn{2}{c}{gpuBatchMatrix} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
Parameter & Estimate & 95\% CI & Estimate & 95\% CI\\
\midrule
range & 38618.730 & (21805.93, 68394.54) & 38618.730 & NA\\
sdNugget & 0.992 & (0.684,1.439) & 0.992 & NA\\
shape & 1.826 & (-0.574,4.227) & 1.826 & NA\\
anisoRatio & 8.092 & (5.321,12.305) & 8.092 & NA\\
anisoAngleRadians & 0.652 & (0.595, 0.709) & 0.652 & NA\\
boxcox & 0.496 & (0.373,0.620) & 0.496 & NA\\
\bottomrule
\end{tabular}
\end{table}

@@

{\centering \includegraphics[width=0.5\linewidth]{profile_logl_swiss}

@@

{\centering \includegraphics[width=1\linewidth]{swiss_pro_4}

>>>>

\caption{\label{tab:swisssummarycompare}Summary comparison}
\centering
\begin{tabular}[t]{rcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{geostatsp} & \multicolumn{2}{c}{gpuBatchMatrix} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
Parameter & Estimate & 90\% CI & Estimate & 90\% CI\\
\midrule
range & 38618.730 & (18544.14 ,80424.68) & 38618.730 & (24202.12, 130428.60)\\
sdNugget & 0.992 & (0.615,1.599) & 0.992 & (0, 1.236)\\
shape & 1.826 & (-1.255,4.907) & 1.826 & (4.540, 6.000)\\
anisoRatio & 8.092 & (4.725,13.386) & 8.092 & (4.721, 14.124)\\
anisoAngleRadians & 0.652 & (0.578, 0.725) & 0.652 & (0.567,0.723)\\
boxcox & 0.496 & (0.375,0.655) & 0.496 & (0.403, 0.628)\\
\bottomrule
\end{tabular}
\end{table}

@@

{\centering \includegraphics[width=0.5\linewidth]{profile_logl_swiss} 
\includegraphics[width=0.5\linewidth]{betaprofile}

@@

{\centering \includegraphics[width=0.5\linewidth]{swiss_pro_4}

{\centering \includegraphics[width=0.5\linewidth]{swiss_pro_2}
